\documentclass{scrartcl}

\usepackage[utf8]{inputenc}

\usepackage{natbib}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{listings}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
% \usepackage{parskip}
% \setlength{\parskip}{10pt}
\usepackage{tikz}
\usetikzlibrary{arrows, decorations.markings}
\usepackage{chngcntr}
\counterwithout{figure}{section}


\begin{document}

\begin{titlepage}

\centering
{\scshape\LARGE Master thesis project proposal}

\vspace{0.5cm}
{\huge\bfseries Source-to-source translation between Agda and Idris
  }

\vspace{2cm}
{\Large Jakob Larsson \texttt{<jakob@karljakoblarsson.com>}}

\vspace{1.0cm}
{\large Suggested Supervisor at CSE: Patrik Jansson }

% \vspace{1.5cm}
\vspace{1.5cm}
{\large Relevant completed courses:}

{\itshape
Types for Programs and Proofs, DAT350 \\
Advanced Functional programming, TDA342 \\
}

\vfill
{\large \today}

\end{titlepage}

% \section{Introduction}

Agda~\cite{agda} and Idris~\cite{idris} are two dependently typed programming
languages.  Agda is mainly focused on logical soundness and theorem proving
while Idris prioritizes general purpose programming ahead of proofs. However,
even with different focus and priorities they have much in common, and their
features and type systems are similar.

We wish to investigate if it is possible to construct a source to source
translation of a common subset between the languages. This would allow
libraries to be reused in both languages. A Idris program may be more easily
proved in Agda, and a well proven Agda library can use Idris to develop an
interface to the outside world.  It will also increase confidence if a given
proof or program is valid in both languages.


A start is to compile simple expressions for Int or something similar. And
show that it can be done. If everything goes well we can use the SDP library
IdrisLibs as a huge project to test on.
Start with normal types and functions for simple lambda functions over Int or
Nat.

A small start is to just transpile small functions with non-dependent types
over Nat for example. The we can develop the implementation to support bigger
types and then follow with dependent types.  Functionality which is not
available in both languages could be represented by holes. That way the user
can 'easily' implement whats missing.

To test the implementation we need actually used code. A good choice is to use
the Sequential Decision Problem library IdrisLibs
~\footnote{https://gitlab.pik-potsdam.de/botta/IdrisLibs} which is one of the
biggest Idris codebase available. This will guide our implementation by first
supporting the features used in the core parts of IdrisLibs. And then work to
support more and more of the library.

A challenge is to find the biggest common subset of the languages. A useful
transpiler needs to support most widely used features. But there are
differences between Agda and Idris.


% ~\cite{sdpcontrib}



% \section{Goals and Challenges}

% \section{Approach}



\bibliographystyle{plain}

\bibliography{sfeeca}

\end{document}
