\documentclass{scrartcl}

\usepackage[utf8]{inputenc}

\usepackage{natbib}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{listings}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
% \usepackage{parskip}
% \setlength{\parskip}{10pt}
\usepackage{tikz}
\usetikzlibrary{arrows, decorations.markings}
\usepackage{chngcntr}
\counterwithout{figure}{section}


\begin{document}

\begin{titlepage}

\centering
{\scshape\LARGE Master thesis project proposal}

\vspace{0.5cm}
{\huge\bfseries SDP something something
  }

\vspace{2cm}
{\Large Jakob Larsson \texttt{<jakob@karljakoblarsson.com>}}

\vspace{1.0cm}
{\large Suggested Supervisor at CSE: Patrik Jansson }

% \vspace{1.5cm}
\vspace{1.5cm}
{\large Relevant completed courses:}

{\itshape
Types for Programs and Proofs, DAT350 \\
Advanced Functional programming, TDA342 \\
}

\vfill
{\large \today}

\end{titlepage}

% \section{Introduction}

% \section{Goals and Challenges}

% \section{Approach}


Development of SDP to use interfaces/typeclasses in Idris 2

IdrisLib is an implementation of SDP theory in Idris. It is currently based on
Idris wholes which is not optimal from a usability standpoint. Idris Interfaces
or type classes as they are called in Haskell has several advantages. You can
have several problems instaniated in the same module for example.

Idris 2 development is comming along which can also be used for a new and great
implementation.

So the question is to port IdrisLibs to Idris 2 and hopefully the world will be
great again. Or something like that.

Sequential Decision Problems is the problem of finding optimal controls for
a probleb with rewards and large state space. IdrisLibs has a implementation of
it.

The current implementation is built upon Idris holes, because typeclasses were
not very well supported when the implementation happend. But now they are
better supported so we should use them to have a better implementation.

TODO: implement the SDP IdrisLib with type classes instead of holes. You may
want several problems implemented in the same module for example. To compare
them.

Finiteness and Decidability.

The users also have to implement similar boilerplate code over and over. How
can this be reduced without sacrificing generalness.

https://gitlab.pik-potsdam.de/botta/IdrisLibs
~\cite{sdpcontrib}
~\cite{sdpcomp}


\bibliographystyle{plain}

\bibliography{sfeeca}

\end{document}
